# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r echo=TRUE}
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", destfile="repdata-data-activity.zip",method="curl")
unzip("repdata-data-activity.zip")
activity <- read.csv("activity.csv")
library(reshape)
library(reshape2)
library(ggplot2)
library(lattice)
```
## What is mean total number of steps taken per day?
```{r echo=TRUE}
amdmelt <- melt(activity, id="date", measure.vars=c("steps","interval"))
amdcast <- dcast(amdmelt, date~variable, sum)
qplot(steps, data=amdcast, geom="histogram")
mean(amdcast$steps, na.rm=TRUE)
median(amdcast$steps, na.rm=TRUE)
```
## What is the average daily activity pattern?
```{r echo=TRUE}
amdmelt2 <- melt(activity, id="interval", measure.vars="steps", na.rm=TRUE)
amdcast2 <- dcast(amdmelt2, interval~variable, mean)
adap <- ggplot(amdcast2, aes(interval,steps))
adap + geom_line()
maxamdcast2 <- amdcast2[amdcast2$steps==max(amdcast2$steps),]
maxamdcast2$interval
```
## Imputing missing values
```{r echo=TRUE}
activity[is.na(activity)] <- amdcast2$steps
amdmelt3 <- melt(activity, id="date", measure.vars=c("steps","interval"))
amdcast3 <- dcast(amdmelt3, date~variable, sum)
qplot(steps, data=amdcast3, geom="histogram")
mean(amdcast3$steps)
median(amdcast3$steps)
```
###The mean hasn't changed, but the median has.

## Are there differences in activity patterns between weekdays and weekends?
```{r echo=TRUE}
activity$date <- as.Date(activity$date, format="%Y-%m-%d")
activity$day <- format(activity$date, "%a")
activity$weekend <- factor(ifelse(activity$day=="Sat"|activity$day=="Sun","weekend","weekday"))  
airquality <- transform(airquality, Month=factor(Month))
actagg <- aggregate(steps~interval+weekend, data=activity, mean)
adap <- ggplot(actagg, aes(interval,steps))
adap + geom_line() + facet_grid(weekend~.)
```
### Or, in line with the lattice plot shown in the assignment directions:
```{r echo=TRUE}
xyplot(steps ~ interval | weekend, data=actagg, type="l", layout=c(1,2))
```